Stateless Model Checking with Data-Race Preemption Points

### 2016-07-16 oopsla-16/warpzone.tex
Last of garth's commence
bit extra future work

% TODO CAMREADY: Measure how much subset overlap there is.
{\bf Avoiding redundant work.}
When we extend a small state space with more PPs, the new state space is guaranteed to test a superset of interleavings compared to the old one.
Any interleaving which does not preempt threads on any of the new PPs will be repeated work.
%Because we prioritize completing small state spaces before extending them with more PPs,
%the superset state spaces we run later will repeat each branch of their already-completed subsets.
%
%We measured the proportion of repeated work among completed state spaces across our test suite;
%on average, {\bf \large 999\%} of the interleavings in each test were repeated, with some tests as high as {\bf \large 9999\%}.
This may make us slower than SSS-MC to find certain bugs,
for example, if both {\tt lock} and {\tt unlock} PPs together expose a bug, but not either alone.
%Similarly, when pursuing total verification (\sect{\ref{sec:totalverif}}),
%if the state space resulting from preempting on every instruction could be completed,
%an SSS-MC tool such as \cite{spin} might achieve that verification faster,
%as Iterative Deepening will test many subsets of data-race PPs first.
Predicting whether an upcoming interleaving has already been tested is not straightforward,
but we believe future implementations
%of Iterative Deepening
could incorporate cross-job memoization
to prune some or all such repeated work.

@@

\revision{
{\bf Integration with static data-race analysis.}
In \sect{\ref{sec:eval-sssmc}}, we evaluated SSS-MC's ability to find data-race-induced failures
by configuring a static predicate to preempt on any non-stack memory access.
This introduced up to thousands of new PPs on each new test execution, with a prohibitive performance impact.
While this performance could be improved by
%relaxing the preemption strategy,
instead using a static or single-pass analysis to find data-race candidate PPs in advance \cite{portend},
this strategy sacrifices the soundness of the verification guarantee, as shown in \sect{\ref{sec:eval-dr}}.
However, \quicksand~itself could employ static data-race analysis \cite{racerx} in future work.
Statically-identified data race candidates could heuristically be included in our ``seed'' PP sets (\sect{\ref{sec:initial-pp}}),
enabling \quicksand~to focus on the most suspicious races immediately, rather than waiting for them to be identified after potentially many iterations of MC.
}

>>>>

% TODO CAMREADY: Measure how much subset overlap there is.
{\bf Avoiding redundant work.}
When we extend a small state space with more PPs, the new state space is guaranteed to test a superset of interleavings compared to the old one.
Any interleaving which does not preempt threads on any of the new PPs will be repeated work.
%Because we prioritize completing small state spaces before extending them with more PPs,
%the superset state spaces we run later will repeat each branch of their already-completed subsets.
%
%We measured the proportion of repeated work among completed state spaces across our test suite;
%on average, {\bf \large 999\%} of the interleavings in each test were repeated, with some tests as high as {\bf \large 9999\%}.
This may make us slower than SSS-MC to find certain bugs,
for example, if both {\tt lock} and {\tt unlock} PPs together expose a bug, but not either alone.
%Similarly, when pursuing total verification (\sect{\ref{sec:totalverif}}),
%if the state space resulting from preempting on every instruction could be completed,
%an SSS-MC tool such as \cite{spin} might achieve that verification faster,
%as Iterative Deepening will test many subsets of data-race PPs first.
Predicting whether an upcoming interleaving has already been tested is not straightforward,
but we believe future implementations
%of Iterative Deepening
could incorporate cross-job memoization
to prune some or all such repeated work.
\revisionx{Prioritizing the maximal state space in particular could also improve completion times:
whenever the maximal job finishes with no new data-races, future implementations could immediately prune all subset jobs and declare a total verification.}

@@

\revision{
{\bf Integration with static data-race analysis.}
In \sect{\ref{sec:eval-sssmc}}, we evaluated SSS-MC's ability to find data-race-induced failures
by configuring a static predicate to preempt on any non-stack memory access.
This introduced hundreds of new PPs on each new test execution, with a prohibitive performance impact.
While this performance could be improved by
%relaxing the preemption strategy,
instead using a static or single-pass analysis to find data-race candidate PPs in advance \cite{portend},
this strategy sacrifices the soundness of the verification guarantee, as shown in \sect{\ref{sec:eval-dr}}.
However, \quicksand~itself could employ static data-race analysis \cite{racerx} in future work.
Statically-identified data race candidates could heuristically be included in our ``seed'' PP sets (\sect{\ref{sec:initial-pp}}),
enabling \quicksand~to focus on the most suspicious races immediately, rather than waiting for them to be identified after potentially many iterations of MC.
}
